Inequality in consumption

### 2017-04-13 ms2/ms2.Rmd
ms2 start

---
title: "Inequality in consumption"
author: "Scott Olesen"
date: "2/22/2017"
output: html_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=7, fig.height=4, fig.path='fig/',
                      echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE)
```

# Background

What is the inequality in consumption for antibiotics? How does it depend on region or the antibiotic used?

# Methods

I define the Juran inequality index $J$: for a random variable $X$ with a domain $\{0, 1\}$ and a cumulative distribution function $F_X$, $J(X)$ is that value such that $F(J(X)) = 1 - J(X)$. For example, if the top 20% of beneficiaries make 80% of the claims, then $J = 0.8$.

For each group under consideration, I considered 5 different metrics:

- the fraction of beneficiaries with at least one claim
- the Juran index among all beneficiaries
- the Juran index among beneficiaries with at least one claim
- the Gini index among all beneficiaries
- the Gini index among beneficiaries with at least one claim

```{r setup}
library(ineq)
is_nonzero = function(x) x > 0
nonzero = function(x) x[is_nonzero(x)]
fraction_nonzero = function(x) sum(is_nonzero(x)) / length(x)
gini = function(x) ineq(x, type='Gini')

@@

add_zeros = function(x, n) {
  if (n < length(x)) {
    stop(sprintf('cannot extend x of length %i to %i', length(x), n))
  }

  c(x, rep(0, n - length(x)))
}

summarize_claims = function(x) {
  summarize(x, n_claims=sum(n_claims), n_days=sum(days_supply)) %>%
    mutate(n_days=if_else(is.na(n_days), 0L, n_days))
}

summarize_inequality = function(x, ...) {
  do(x, inequalities(., ...))
}

@@

```{r load_data}
usage = read_tsv('../bene_usage_2011.tsv')
```

>>>>

---
title: "Inequality in consumption"
author: "Scott Olesen"
output: html_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=7, fig.height=4, fig.path='fig/',
                      echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE)
import::from(ineq, Gini)
```

```{r setup}
is_nonzero = function(x) x > 0
nonzero = function(x) x[is_nonzero(x)]
fraction_nonzero = function(x) sum(is_nonzero(x)) / length(x)

@@

klasma = function(x, threshold) {
  if (!between(threshold, 0.0, 1.0)) stop("bad threshold")
  data_frame(x=x) %>%
    mutate(cdf=cume_dist(x)) %$%
    { sum(x[cdf >= threshold]) / sum(x) }
}

@@

```{r compute_inequalities}
bene = read_tsv('../

usage = read_tsv('usage_2011.tsv')
```
